---
title: "GSE80080"
output: html_document
date: "2023-09-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis of microarray data from GSE80080

```{r}
library(limma)
library(knitr)
library("illuminaio")

bgxfile = dir(path="./", pattern="bgx")
idatfiles = dir(path="./GSE80080_RAW", pattern=".idat", full.names = T)
# idatfiles = idatfiles[-4] # removing RXF2
data = read.idat(idatfiles, bgxfile)
data$other$Detection <- detectionPValues(data)

```




```{r}
pe = propexpr(data)
kable(pe, "markdown") # proprotion of probes being detected as expressed, should be consistent
```




```{r}
data.norm = neqc(data) # normalize data
# table(apply(data.norm$other$Detection, 1, function(x){all(x < 0.05)}))

data.norm

```


```{r}
eset = data.norm$E
distance = dist(t(eset))#,method="maximum")
clusters = hclust(distance, method="ward.D")
plot(clusters) 
```


```{r}
sampledata = data.frame(geo=c("GSM2112539", "GSM2112540", "GSM2112541", "GSM2112542", "GSM2112543", "GSM2112544"),
						name = c("SKR_1", "RXF_1", "SKR_2", "RXF_2", "SKR_3", "RXF_3"),
						condition = c("SKR", "RXF", "SKR", "RXF", "SKR", "RXF")
						)

#without RXF 2
# sampledata = data.frame(geo=c("GSM2112539", "GSM2112540", "GSM2112541", "GSM2112543", "GSM2112544"),
# 						name = c("SKR_1", "RXF_1", "SKR_2", "SKR_3", "RXF_3"),
# 						condition = c("SKR", "RXF", "SKR", "SKR", "RXF")
# 						)
```


```{r}
library(ggplot2)

pca = prcomp(t(eset))
percentVar <- round(100*pca$sdev^2/sum(pca$sdev^2))
data = as.data.frame(pca$x)
data$name = sampledata$name
data$condition = sampledata$condition
ggplot(data, aes(PC1, PC2, colour=condition)) + geom_point(size=3) +
  scale_x_continuous(paste0("PC1: ",percentVar[1],"% variance"), limits=c(-45, 45))  + 
  scale_y_continuous(paste0("PC2: ",percentVar[2],"% variance"), limits=c(-45, 45)) +
  coord_fixed() + theme_classic() + geom_text(data = data, aes(PC1,PC2, label = name), hjust = 1.2)
```


```{r}
condition <- factor(sampledata$condition, unique(sampledata$condition))
design <- model.matrix(~0 + condition)
colnames(design) <- c("SKR", "RXF")
head(design) # design matrix: ???
```



```{r without unexpressed probes}

# table(apply(data.norm$other$Detection, 1, function(x){any(x < 0.05)})) # how many are expressed

# data.norm.filtered = data.norm[apply(data.norm$other$Detection, 1, function(x){any(x < 0.05)}),] # expressed in any sample
data.norm.filtered = data.norm[(rowSums(data.norm$other$Detection < 0.05) >= 3),] # expressed in at least 3 samples

```

```{r without the probes without genes}
table(table(data.norm$genes$Symbol))

 
empty_probes = c(which(data.norm.filtered$genes$Symbol == ""), which(data.norm.filtered$genes$Symbol == " "), which(is.na(data.norm.filtered$genes$Symbol)))
data.norm.filtered$genes = data.norm.filtered$genes[-empty_probes,]
nrow(data.norm.filtered$genes)

remove_empty_probes <- function(E, genes){
  
  print(dim(E))
  E_remove = c()
  for (i in seq(length(rownames(E)))){
    if (!(rownames(E)[i] %in% genes$Array_Address_Id)){
      E_remove = c(E_remove, i)
    }
  }
  E = E[-E_remove,]
  print(dim(E))
  return(E)
}

data.norm.filtered$E = remove_empty_probes(data.norm.filtered$E, data.norm.filtered$genes)
nrow(data.norm.filtered)




```

```{r without redundant probes}

#n
# empty_probes = c(which(data.norm.filtered$genes$Symbol == ""), which(data.norm.filtered$genes$Symbol == " "), which(is.na(data.norm.filtered$genes$Symbol)))
# x = data.norm.filtered$genes[-empty_probes,]

widest_range_access = c()
all_repeat_access_ids = c() # all access IDs associated with repeated genes 
for (i in unique(data.norm.filtered$genes$Symbol[which(duplicated(data.norm.filtered$genes$Symbol))])) {
  quartile_range = c()
  access_id = as.character(data.norm.filtered$genes$Array_Address_Id[data.norm.filtered$genes$Symbol == i]) # collect access IDs of those with multiple gene symbols
  all_repeat_access_ids = c(all_repeat_access_ids, access_id)
  for (t in access_id){ # for every probe, calculate the interquartile range
    quartile_range = c(quartile_range, abs(summary(data.norm.filtered$E[t,])[5] - summary(data.norm.filtered$E[t,])[2]))
  }
  widest_range_access = c(widest_range_access, access_id[which.max(quartile_range)])
}

remove_repeats = all_repeat_access_ids[!(all_repeat_access_ids %in% widest_range_access)]
data.norm.filtered = data.norm.filtered[-(which(rownames(data.norm.filtered) %in% remove_repeats)),]
nrow(data.norm.filtered)

# number of unique genes detected
length(unique(data.norm.filtered$genes$Symbol[data.norm.filtered$genes$Array_Address_Id %in% rownames(data.norm.filtered$E)]))
length(unique(data.norm.filtered$genes$Symbol)) # 18895 genes




```

```{r}
# DE 

fit <- lmFit(data.norm.filtered, design)
contrast.matrix <- makeContrasts(kc_knc = RXF - SKR, levels=design)
kc_fits <- contrasts.fit(fit, contrast.matrix)
kc_ebFit <- eBayes(kc_fits)
results = topTable(kc_ebFit, coef=1, number=nrow(data.norm))
sum(results$P.Value < 0.01) 
# 1196 genes, not accounting for multiple testing (with: all samples, expressed genes at (any < 0.05), no empty probes and repeat probes with lower interquartile range)
# 1527 genes, not accounting for multiple testing (with: all samples, expressed genes in at least 3 samples. no empty probes and repeat probes with lower interquartile range)
# 800 genes, not accounting for multiple testing (with: excluding RXF2, expressed genes at (any < 0.05), no empty probes and repeat probes with lower interquartile range)
# 1079 genes, not accounting for multiple testing (with: excluding RXF2, expressed genes in at least 3 samples. no empty probes and repeat probes with lower interquartile range)



sum(results$P.Value < 0.1) 
# 5102 genes, not accounting for multiple testing (with: all samples, expressed genes at (any < 0.05), no empty probes and repeat probes with lower interquartile range)
# 4930 genes, not accounting for multiple testing (with: all samples, expressed genes in at least 3 samples. no empty probes and repeat probes with lower interquartile range)
# 4401 genes, not accounting for multiple testing (with: excluding RXF2, expressed genes at (any < 0.05), no empty probes and repeat probes with lower interquartile range)
# 4308 genes, not accounting for multiple testing (with: excluding RXF2, expressed genes in at least 3 samples. no empty probes and repeat probes with lower interquartile range)


sum(results$adj.P.Val < 0.1) 
# 299 with: all samples, expressed genes at (any < 0.05), no empty probes and repeat probes with lower interquartile range
# 1655 with: all samples, expressed genes in at least 3 samples, no empty probes and repeat probes with lower interquartile range -- YAY
# 0! with: without RXF2, expressed genes at (any < 0.05), no empty probes and repeat probes with lower interquartile range
# 577 with: all samples, expressed genes in at least 3 samples, no empty probes and repeat probes with lower interquartile range

de_results = results[results$adj.P.Val < 0.1,]
de_up_results = de_results[de_results$logFC > 0,] # upregulated genes
de_down_results = de_results[de_results$logFC < 0,] # downregulated genes

sum(de_results$logFC > 0)
hist(de_results$logFC)


hist(results$P.Value, xlab="pvalue", main="") 
hist(results$adj.P.Val, xlab="pvalue", main="") 

```



```{r GSEA of all expressed genes}

library(fgsea)


pathways <- c(gmtPathways("h.all.v2023.1.Hs.symbols.gmt"), gmtPathways("c2.cp.v2023.1.Hs.symbols.gmt")) 


changes_lfc = results$logFC
names(changes_lfc) = results$Symbol

changes_lfc = changes_lfc[order(changes_lfc, decreasing=TRUE)] #ranked list
head(changes_lfc)
head(pathways)

fgseaRes <- fgsea(pathways = pathways, 
                  stats = changes_lfc,
                  minSize=15,
                  maxSize=500) #to generate p-value

head(fgseaRes[order(pval), ], n = 9)
sum(fgseaRes$padj < 0.1)

changing_pathways = fgseaRes[fgseaRes$padj < 0.1,]
changing_pathways$pathway

```

# Pathway 1: Hallmark Epithelial Mesenchymal Transition 

EXPLANATION: 
```{r}

plotEnrichment(pathways[[changing_pathways$pathway[1]]], changes_lfc, ticksSize = 1) + labs(title=changing_pathways$pathway[1])

```



# Pathway 2: Hallmark Hypoxia

EXPLANATION: 
```{r}

plotEnrichment(pathways[[changing_pathways$pathway[2]]], changes_lfc, ticksSize = 1) + labs(title=changing_pathways$pathway[2])

```

# Pathway 3: Hallmark TNFA Signaling via NFKB

EXPLANATION: 
```{r}

plotEnrichment(pathways[[changing_pathways$pathway[3]]], changes_lfc, ticksSize = 1) + labs(title=changing_pathways$pathway[3])

```

# Pathway 4: KEGG Pathways in Cancer

EXPLANATION: 
```{r}

plotEnrichment(pathways[[changing_pathways$pathway[4]]], changes_lfc, ticksSize = 1) + labs(title=changing_pathways$pathway[4])

```


# Pathway 5: NABA Matrisome

EXPLANATION: 
```{r}

plotEnrichment(pathways[[changing_pathways$pathway[5]]], changes_lfc, ticksSize = 1) + labs(title=changing_pathways$pathway[5])

```

# Pathway 6: NABA Matrisome Associated

EXPLANATION: 
```{r}

plotEnrichment(pathways[[changing_pathways$pathway[6]]], changes_lfc, ticksSize = 1) + labs(title=changing_pathways$pathway[6])

```

# Pathway 7: PID FRA Pathway

EXPLANATION: 
```{r}

plotEnrichment(pathways[[changing_pathways$pathway[7]]], changes_lfc, ticksSize = 1) + labs(title=changing_pathways$pathway[7])

```

# Pathway 8: WP Adipogenesis

EXPLANATION: 
```{r}

plotEnrichment(pathways[[changing_pathways$pathway[8]]], changes_lfc, ticksSize = 1) + labs(title=changing_pathways$pathway[8])

```


# Pathway 9: WP Nuclear Receptors Metapathway

EXPLANATION: 
```{r}

plotEnrichment(pathways[[changing_pathways$pathway[9]]], changes_lfc, ticksSize = 1) + labs(title=changing_pathways$pathway[9])

```


```{r ClusterProfiler / GO -- UPREGULATED}

## loading in libraries
library(pheatmap)
library("grid")
# library("gridExtra")
library(cluster)

rld_up = data.norm.filtered$E[data.norm.filtered$E$Array_Address_Id %in% rownames(de_up_results)]
# rld_signif = assay(rld)[rownames(de_up_results),]
rld_z = t(apply(rld_up, 1, function(x){ (x - mean(x)) / sd(x)})) # converting to zscore --> to scale
# Converting the values to z-scores allows us to group the genes by similar pattern of change

#This allows us to get a better understanding of the distribution of patterns of change.   
thr = 3 # threshold on z-score
rld_z[rld_z > thr] = thr # anything greater than 3 --> just 3
rld_z[rld_z < -thr] = -thr # anything less than 3 --> just -3


# elbow criterion - choosing K
set.seed(123)
k.max <- 20 # number of replicates/samples (N = k)
wss <- sapply(2:k.max, 
              function(k){kmeans(rld_z, k, nstart=10,iter.max = 15 )$tot.withinss})
plot(2:k.max, wss,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares",
     xlim = c(0, 20))
# Choosing K: K should be around 4 clusters because this is when the variation 
# accounted for begins to plateau according to the elbow criterion


# How well does each gene belong in its cluster: Silhouette
SIL = sapply(2:20, function(i) { 
  #print(i)
  results.coef.kmeans =  kmeans(rld_z, i, nstart=50, iter.max=50)
    mean(silhouette(results.coef.kmeans$cluster, dist(rld_z))[,3]) }) # average fit of each gene within a cluster
plot(c(0,SIL), type="b") #elbows at around 6, indicating the 6 may be the most appropriate k


# Testing 7 clusters
k = 5
results.coef.kmeans =  kmeans(rld_z, k, nstart=10, iter.max=50)


x = silhouette(results.coef.kmeans$cluster, dist(rld_z))
plot(x, col="black", border=NA, main=paste("k = ", k, collapse = "")) # Silhoutte plot
table(results.coef.kmeans$cluster) # how many genes fit per cluster


## heatmap by cluster
results.coef = rld_z[order(results.coef.kmeans$cluster),] # gets rid of scale, allows us to focus on 
#only the pattern of expression changes
indicator = results.coef.kmeans$cluster[order(results.coef.kmeans$cluster)]
color = c(colorRampPalette(c("mediumblue", "white"))(14), colorRampPalette(c("white", "firebrick2"))(14))
breaksList = seq(-3, 3, length.out = 29)
heat.map <- pheatmap(results.coef, cluster_col=FALSE, breaks=breaksList, 
                     cluster_rows=FALSE, show_rownames=FALSE,color = color,
                     fontsize_row = 3, legend=TRUE,border_color = NA, main = "upregulated genes")
grid.newpage()
grid.draw(heat.map$gtable)


```







How do we get this to be better? (TO DO by Sept 28)
# use this to filter de_mirna_up_targets to only show genes expresed in muscle
# [SKIP] try running this again without RXF 2
# [DONE]filter results df to remove the ones without genes 
# [done I THINK?] filter to use only one probe per gene --> which probe to use? --> pick probe with highest interquartile range (most variable)

TO DO by Oct 5:
# Take ALL EXPRESSED genes and put them in GSEA --> do not use GO and clusterprofiler
# [DONE] remove the probes without expression --> detectionpvalues() --> figure out propexpr cutoff (? 0.05)
# [DONE] try all 3filter steps with and without RXF 2

TO DO by Oct
# Run clusterprofiler & GO on all 
# Look at the different pathways with padj < 0.1 --> vaildate this dataset, is this useful?
# run clusterprofiler on up and downregulated genes separately
# filter miRNA de with genes de --> enrichment analysis, fold changes of genes, context score filters


```{r}
sessionInfo()
```